Unveiling the Syntax Within: Interpreting Grammar Embeddings in Meta’s LLaMA Models

### 2025-02-23 paper/main.tex
abstract

\author{%
  Pratim Chowdhary\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Dartmouth College\\
  \texttt{cpratim.25@dartmouth.edu} \\
  % examples of more authors
  \And
  Peter Chin \\
  Department of Engineering\\
  Thayer School of Engineering\\
  \texttt{pc@dartmouth.edu} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph.
\end{abstract}

@@

Please read the instructions below carefully and follow them faithfully.

>>>>

\author{%
  Pratim Chowdhary\thanks{Use footnote for providing further information
    about author (webpage, alternative address)---\emph{not} for acknowledging
    funding agencies.} \\
  Department of Computer Science\\
  Dartmouth College\\
  \texttt{cpratim.25@dartmouth.edu} \\
  % examples of more authors
  \And
  Peter Chin \\
  Department of Engineering\\
  Thayer School of Engineering\\
  \texttt{pc@dartmouth.edu} \\
  \And
  Deepernab Chakrabarty \\
  Department of Computer Science\\
  Dartmouth College\\
  \texttt{deepernab@dartmouth.edu} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
}

@@

\begin{abstract}
  This paper investigates the mechanisms by which large language models (LLMs) encode 
  grammatical knowledge, focusing on Meta's LLaMA models. By leveraging embedding vectors, 
  we classify grammatically correct sentences and analyze the activation patterns of 
  attention heads to identify their roles in processing specific grammatical structures. 
  Furthermore, we explore the effects of selectively removing these attention heads, shedding 
  light on how grammar is embedded within the model's architecture. Our findings aim to enhance
  the understanding of LLMs' linguistic capabilities and their internal organization of syntactic knowledge.
\end{abstract}

@@

Please read the instructions below carefully and follow them faithfully. fds
